\vfill A Testing Framework for Web Applications

### 2014-02-28 Paper/paper.tex
Travis updates, Semaphore start

\paragraph{Pros}

\paragraph{Cons}

@@

Travis requires that your projects be hosted on GitHub, but by doing so the setup is incredibly easy. You sign into Travis using your GitHub credentials and Travis pulls up all of your repositories automatically. Getting a project running with Travis is fairly easy; you just create a yml file in your repository. I was able to set up everything I needed in six very simple lines.

Travis comes with incredibly thorough documentation and a wealth of built-in services like databases, notifications, deployment options, and GUI/Headless browsers. Travis supports all of the most popular databases: MySql, PostgreSql, MongoDB, CouchDB, and a myriad of others. It offers a number of notification options ranging from Email to IRC to HipChat (a chat service from Atlassian). Travis offers deployment to just about every sort of provider there is, from Heroku to AWS S3 to RubyGems and also provides the ability to create custom hooks to deploy to a provider not supported natively.

@@

From what I gathered, Travis appears to be targeted at companies, not individual developers but works great if you are willing to open-source your repositories.

@@

Travis
- Free for public
- Paid for private
- GitHub only
- Requires .travis.yml file

@@

Jenkins
- Free all the time forever because you set it up
- It'll do everything....? 
- Lots of setup

\paragraph{Pros}

\paragraph{Cons}

@@

\paragraph{Pros}

\paragraph{Cons}

\subsubsection{Semaphore}

\paragraph{Pros}

\paragraph{Cons}

>>>>

@@

Travis comes with internal support for eleven different languages including Node.JS, Ruby, Java, Python, and more. Travis has incredibly thorough documentation and a wealth of built-in services to work with your project if needed. Services like databases, notifications, deployment options, and GUI/Headless browsers. Travis supports all of the most popular databases: MySql, PostgreSql, MongoDB, CouchDB, and a myriad of others. It offers a number of notification options ranging from Email to IRC to HipChat (a chat service from Atlassian). Travis also offers deployment to just about every sort of provider there is, from Heroku to AWS S3 to RubyGems and also provides the ability to create custom web hooks to deploy to a provider not supported natively.

If at any point your project requires something that Travis does not support natively, you are given the permissions necessary to install any sort of libraries or services that can be installed with apt-get on an Ubuntu machine.

Travis requires that your projects be hosted on GitHub, but by doing so the setup is incredibly easy. You sign into Travis using your GitHub credentials and Travis pulls up all of your repositories automatically.

Getting a project running with Travis is fairly easy; you just create a yml file in your repository with certain lines pertaining to the language, needed services, commands to run, etc. I was able to set up everything I needed in six simple lines.

@@

From what I gathered, Travis appears to be targeted at companies, not individual developers. Travis requires you to host your projects on GitHub and only supports one process running at a time. However, Travis is incredibly easy to set up, does not require you to have your own server, comes with impressive built-in features, and works wonderfully if you are willing to open-source your repositories and put them on GitHub.

\subsection{Semaphore\cite{Semaphore}}
Semaphore is another online CI framework that connects to GitHub to bring in your projects. Semaphore is made by RenderedText, a software consulting team. Semaphore connects with your public and private repositories but requires a subscription after 30 days no matter which repositories you use.

Semaphore was originally designed for only Ruby applications but in January of 2014 they annouced support for Node.js and Javascript and as of February 26th they now offer support for Clojure projects.\cite{SemaphoreBlog} FEATURES, DEPLOYMENT OPTIONS, ETC

@@

@@

\subsubsection{Magnum}

\subsubsection{Drone.io}

@@
